---
title: "Alcohol vs Seat choice"
author: "Thomas Matthews"
date: "Spring 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

This plot shows that the people in the back consume more alcohol than the people in the front and middle rows. 


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The people in the back drink more alcohol than the people in the front and middle. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
the p value is 0.000116. It is such a small number that it is unlikely that alcohol consumption in all seats is the same. 



## When significant follow up with TukeyHSD  

```{r}
plot(TukeyHSD(model1))
```
People who sit in the back row drink more than the people who sit in the front row. There is no difference in alcohol consumption between the people who sit in the front and middle. 




## Conclusions






